### 2020-03-30 papers.tex
papers.tex: Embiggen track title for better flow
Fix paper title misspelling

\addtrack
	{}{Artificial Intelligence \& Machine Learning}
\addpaper
	{Image2image neural network for addition and subtraction evaluation of a pair of not very large numbers}
	{Vladimir Ivashkin}
	{Keywords: neural network, computer vision, calculator}
	{SIGBOVIK_2020_paper_6}
	{0cm}
	{}
\addpaper
	{Robot ethics:\@ Dangers of reinforcement learning}
	{Jake Olkin}
	{Keywords: deep reinforcement learning, ethics, simulation, spoof}
	{SIGBOVIK_2020_paper_24}
	{0cm}
	{}
\addpaper
	{Learning to be wrong via gradient ascent: A broken clock is right twice a day, but a clock that runs backwards can be used to tell the time!}
	{Alex Meiburg}
	{Keywords: machine learning, gradient descent, loss landscape, logistic regression, biased estimators, eliminating bias, overtraining}
	{SIGBOVIK_2020_paper_35}
	{0cm}
	{}
\addpaper
	{GradSchoolNet:\@ Robust end-to-end *-shot unsupervised deepAF neurla attention model for convexly optimal (artifically intelligent) success in computer vision research}
	{Divam Gupta, Varun Jain}
	{Keywords: none, haha, nono}
	{SIGBOVIK_2020_paper_17}
	{1.8cm}
	{}
\addreview{SIGBOVIK_2020_review_10}{0cm}

@@

\addtrack
	{}{The SIGBOVIK 2020 Field Guide to Conspiracy Theories}
\addpaper
	{Faking ancient computer science:\@ A special SIGBOVIK tutorial}
	{Roxanne van der Pol, Brian van der Bijl, Diederik M.\@ Roijers}
	{Keywords: ancient computer science, aliens, conspiracy theories, Triangle of Conspiracy Succession, probability, Arcaicam Esperantom, random number generator, pseudo-science}
	{SIGBOVIK_2020_paper_7}
	{0cm}
	{}
\addpaper
	{MORSE OF COURSE:\@ Paper reveals time dimension wasted}
	{Dougal Pugson}
	{Keywords: Morse code, performance, Bash, protocols}
	{SIGBOVIK_2020_paper_26}
	{0cm}
	{}
\addpaper
	{The Pacman effect and the Disc-Sphere Duality}
	{Francisco Ferreira, Fulvio Gesmundo, Lorenzo Gheri, Pietro Gheri, Riccardo Pietracaprina, Fangyi Zhou}
	{Keywords: Pacman, peace, Earth, flat, round, disc, sphere}
	{SIGBOVIK_2020_paper_37}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_4}{0cm}

>>>>

\addtrack
	{}{Artificial Intelligence \& Machine Learning}
\addpaper
	{Image2image neural network for addition and subtraction evaluation of a pair of not very large numbers}
	{Vladimir Ivashkin}
	{Keywords: neural network, computer vision, calculator}
	{SIGBOVIK_2020_paper_6}
	{0cm}
	{}
\addpaper
	{Robot ethics:\@ Dangers of reinforcement learning}
	{Jake Olkin}
	{Keywords: deep reinforcement learning, ethics, simulation, spoof}
	{SIGBOVIK_2020_paper_24}
	{0cm}
	{}
\addpaper
	{Learning to be wrong via gradient ascent: A broken clock is right twice a day, but a clock that runs backwards can be used to tell the time!}
	{Alex Meiburg}
	{Keywords: machine learning, gradient descent, loss landscape, logistic regression, biased estimators, eliminating bias, overtraining}
	{SIGBOVIK_2020_paper_35}
	{0cm}
	{}
\addpaper
	{GradSchoolNet:\@ Robust end-to-end *-shot unsupervised deepAF neural attention model for convexly optimal (artifically intelligent) success in computer vision research}
	{Divam Gupta, Varun Jain}
	{Keywords: none, haha, nono}
	{SIGBOVIK_2020_paper_17}
	{1.8cm}
	{}
\addreview{SIGBOVIK_2020_review_10}{0cm}

@@

\addtrack
	{}{\LARGE The SIGBOVIK 2020 Field Guide to Conspiracy Theories}
\addpaper
	{Faking ancient computer science:\@ A special SIGBOVIK tutorial}
	{Roxanne van der Pol, Brian van der Bijl, Diederik M.\@ Roijers}
	{Keywords: ancient computer science, aliens, conspiracy theories, Triangle of Conspiracy Succession, probability, Arcaicam Esperantom, random number generator, pseudo-science}
	{SIGBOVIK_2020_paper_7}
	{0cm}
	{}
\addpaper
	{MORSE OF COURSE:\@ Paper reveals time dimension wasted}
	{Dougal Pugson}
	{Keywords: Morse code, performance, Bash, protocols}
	{SIGBOVIK_2020_paper_26}
	{0cm}
	{}
\addpaper
	{The Pacman effect and the Disc-Sphere Duality}
	{Francisco Ferreira, Fulvio Gesmundo, Lorenzo Gheri, Pietro Gheri, Riccardo Pietracaprina, Fangyi Zhou}
	{Keywords: Pacman, peace, Earth, flat, round, disc, sphere}
	{SIGBOVIK_2020_paper_37}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_4}{0cm}
